Deciding Bitvector Termination with Program Synthesis

### 2014-07-03 papers/termination/paper.tex
First stab at GP

\begin{definition}[Non-Termination Formula - Open Recurrence Set  {\bf [ONT]}]
\label{def:nonterm-formula}
 \begin{align*}
  \exists N, x_0 . \forall x . \exists x' . & I(x_0) \wedge N(x_0) ~ \wedge \\
                                                        & N(x) \rightarrow G(x) ~ \wedge \\
							& N(x) \rightarrow T(x, x') \wedge N(x') 
 \end{align*}
\end{definition}

@@

\subsection{Genetic Programming and Incremental Evolution} \label{sec:gp}

We begin by observing that the asymptotic complexity of all of our synthesis
backends are equal, assuming $P \neq NP$.  This complexity is:

@@

 But it does.
\end{conjecture}

>>>>

\begin{definition}[Non-Termination Formula - Open Recurrence Set  {\bf [ONT]}]
\label{def:nonterm-formula}
 \begin{align*}
  \exists N, x_0 . \forall x . \exists x' . & N(x_0) ~ \wedge \\
                                                        & N(x) \rightarrow G(x) ~ \wedge \\
							& N(x) \rightarrow T(x, x') \wedge N(x') 
 \end{align*}
\end{definition}

@@

\subsection{Genetic Programming and Incremental Evolution} \label{sec:gp}
To generate candidate solutions in the synthesise phase of the refinement loop,
we can use genetic programming (GP).  The general idea is to start with a population
of random programs and evolve a good one.  ``Good'' in this case means that the program
satisfies our specification.  To do this evolution, we compute a fitness for each program
and repeatedly apply genetic operators to the population based on this fitness.  The operators
used are {\sc crossover} and {\sc mutate}.  The crossover operator takes two programs
and combines their code in some what to create a new program.  The mutate operator takes a single
program and randomly changes parts of its code, again creating a new program.  We arrange
things so that the fitter a program is, the more likely it is to be selected as a parent
that will be crossover'd to produce a child in the next generation.  Our fitness function
is just the number of test cases on which the program met the specification.

\iffalse
We begin by observing that the asymptotic complexity of all of our synthesis
backends are equal, assuming $P \neq NP$.  This complexity is:

@@

 But it does.
\end{conjecture}
\fi
